Probabilities of polar aligned disks in binary star systems

### 2024-08-20 src/tex/ms.tex
prepare to rearrange

We can define a function to describe the probability of a polar orbit given the assumption that $\Omega$ is randomly distributed.
\begin{equation}
    \begin{aligned}
        P(j,e_{\rm b}, i) & = 1 - \frac{2}{\pi} \Omega_{\rm min} & \text{if} ~i > i_{\rm crit} \\
        & = 0 & \text{if} ~i \le i_{\rm crit}
    \end{aligned}
\end{equation}

@@

\subsection{An upper limit on the polar fraction}
\label{subsec:fp_limit}
While the true astrophysical distributions of $i$, $e_{\rm b}$, and $j$ are unknown, we can still place constraints on the value of $f_{\rm polar}$.
As discussed previously, if the disk has no preference for coplanar alignment then we can replace $di$ in Equation \ref{fp_int} with $\frac{1}{2}\sin{du_i}du_i$, integrating
from 0 to $pi$.

>>>>

To get the probability of a polar orbit given randomly distributed $\Omega$ we can use a modified version of Equation 8 from \citet{ceppi2024}.
\begin{equation}
    \begin{aligned}
        P(j,e_{\rm b}, i) & = 1 - \frac{2}{\pi} \Omega_{\rm min} & \text{if} ~i > i_{\rm crit} \\
        & = 0 & \text{if} ~i \le i_{\rm crit}
    \end{aligned}
\end{equation}

@@

\subsection{An upper limit on the polar fraction}
\label{subsec:fp_limit}
While the true astrophysical distributions of $i$, $e_{\rm b}$, and $j$ are unknown, we can still place constraints on the value of $f_{\rm polar}$.
As discussed previously, if the disk has no preference for coplanar alignment then we can replace $di$ in Equation \ref{eq:fp_int} with $\frac{1}{2}\sin{du_i}du_i$, integrating
from 0 to $\pi$.
